Systematic Specification for Scalable Verification of Fault-Tolerant Algorithms

### 2016-10-19 doc/om-paper/paper.tex
add figs.

@@

@@

>>>>

\usepackage{graphicx}

@@

We have instantiated the formal model described above to model and verify the classic OM(1) Byzantine fault-tolerant algorithm~\cite{}. OM(1) and its variants have been verified in other settings, allowing us to benchmark our results against others (see Section~\ref{sec:experimental} for experimental results).

The verification is carried out in the Symbolic Analysis Laboratory~\cite{}, which contains a suite of model-checkers and a high-level specification language. In our work, we use the infinite-state model-checker using $k$-induction~\cite{}.

\subsection{OM(1) Overview}

\subsection{Model Sketch}

\subsection{Invariants}

\begin{figure}
  \centering
  \includegraphics[width=8cm]{figs/proof-structure-validity}
  \caption{Proof structure for the validity property.}
  \label{fig:compare}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8cm]{figs/proof-structure-agreement}
  \caption{Proof structure for the agreement property.}
  \label{fig:compare}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=8cm]{figs/benchmark}
  \caption{Comparison of number of nodes vs. verification time.}
  \label{fig:compare}
\end{figure}

% ------------------------------------------------------------
\section{Toward an Architectural Domain-Specific Language}\label{sec:adsl}
